Can machine learning correct microwave humidity radiances for the influence of clouds?

### 2021-02-19 Article/Review_1/response_reviewer_1.tex

\documentclass[11pt,a4paper,draft]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{natbib}
%\usepackage{showframe} %This line can be used to clearly show the new margins

\newgeometry{vmargin={30mm}, hmargin={25mm,25mm}} 
\setlength{\topskip}{0mm}

\begin{document}
	\title{\textbf{Response to Reviewer 1}}
	\date{}
	\maketitle

The authors would like to thank the reviewer for his/her careful review and constructive comments, which we believe will help improve the content of the manuscript.  Below, under each bullet point, we provide a point by point response to each comment/question. The author responses are given in blue, and textual changes are italicised.

\section*{General comments}

@@

\begin{itemize}

\item 	``precipitation and most dense clouds'' I think the hydrometeor size is an important.\\

\textcolor{blue}{Reply: We agree that the hydrometeor size is an important aspect, but when it comes to an overview of the cloud contamination at 183\,GHz, precipitating clouds and clouds with large optical thickness have the strongest effect, and a dense cloud could be composed of hydrometeors of different shapes and sizes. }\\

\item	L66: ``only using measurements (no background data involved)'' My understanding is
		that the method is in theory model-free, but for the demonstration in this study, simulations (e.g. background simulated at MWHS2 frequency) are used. Am I correct?
		Maybe this should be stressed here. Why not try with real MWHS2 observation for the
		all sky dataset?\\

\textcolor{blue}{Reply: Yes, the demonstration of the entire concept is based on simulations. We do not try with the real MWHS-2 observations as the validation of the training process could only be performed against clear-sy simulations. To stress on the fact that only background MWHS-2 observations are used, we have added the following text to Sect. 2.1.1:\\
Pg 4, line 104:
``\textit{For the demonstation of the study, MWHS-2 background or simulations are used. Actual measurements are not taken into account. The requisite data was obtained from ECMWF. More details are described in Sect.2.1.1}.''} \\

\item
		L137 "Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the channel NEDT (Table 1 - Table 3)." Are the errors arising from the radiative transfer calculation accounted for?\\

\textcolor{blue}{Reply: The most important errors arising from radiative transfer calculations, are related to representing the cloud microphysics. In this study, for ICI and SMS, we consider only one particle size distribution (PSD) and habit and this could underestimate the true cloud variability. Underestimation of scattering at higher frequencies can lead to some imperfections in mapping the cloud information from sub-mm and 183\,GHz. Other factors affecting the accuracy of simulations, but not considered due to brevity include neglected antenna pattern and limitations associated with input data, both Cloudsat and ERAInterim. For example, the simulations could have tendency to be biased towards the Cloudsat geographical sampling. The actual background departures and the corresponding bias correction shall only be revealed when data from ICI is available in future.\\
We have added a short description these radiative transfer errors that could affect the simulations in Sect. 2.2.  } \\

\item	
		L159: "for all selected quantile fractions " by quantile fraction, do you mean the n th
		amongst the 7 selected (from 0.2 to 99.8\%)? Also, 16, 50 and 85\% are not symmetric
		(rounding?)\\

\textcolor{blue}{Reply: Yes, the selected quantiles are the seven percentiles mentioned. We re-phrase some sentences here to make it more clear. 85\% is a typo, it should be 84\%. It has been corrected.}\\

\item	
		L163: Pfreundschuh uses an indicator function I (=1 or 0) in the CRPS, the authors
		here use y, can they explain the difference?\\

\textcolor{blue}{Reply: In the study by \citet{pfreundschuh:aneur:18}, CRPS is defined as using an indicator function ($I$), however for QRNN the integral is evaluated only by approximation. To calculate the CRPS, we use a piece-wise linear fit to the approximate posterior CDF obtain from the predicted quantiles. This approximation is further used to calculate CRPS.}\\

\item	
		L173: " The input data is all-sky brightness temperature" the simulated one, even for
		MWHS2, right? \\

\textcolor{blue}{Reply: Yes, even for MWHS-2 we use simulated all-sky brightness temperatures.}\\

\item	L301: "0.15 K" should be -0.15 \\

\textcolor{blue}{Reply: The correction is made.} \\

\item	
		L453: "Among these four channels, 150 GHz has the highest peaking function around 4
		C2km (Chen and Bennartz, 2020)" Could you please clarify what you mean here, 150GHz
		is neither the highest nor the lowest peaking channel nor it peaks at 4km. Channel 89,
		118+/-1.1, 118+/-2.5, and 150 GHz peak at 0.1, 9.6, 2.9, 1km, respectively (according
		to Chen and Bennartz, 2020), this can also be seen in Lawrence et al. (2018) Fig. 1
		through the Jacobians of channels 6 and 7.\\

\textcolor{blue}{Reply: The reviewer is correct. It was wrongly mentioned that 150 GHz is the highest peaking channel, at 4\,km. We have corrected the text and it now reads as:	\\
Pg 25, line 465:	
``\textit{The channels, 150\,GHz and 118.75$\pm$2.5 peak between surface and 4\,km. These channels can only provide coverage to the humidity channels in the lower and mid troposphere. However, the 183\,GHz channels are sensitive to hydrometeor content up to 10\,km. The channel 118.75$\pm$1.1 peaks around 10\,km, but such information is only partly relevant for the higher peaking channels of 183\,GHz.}'' }\\

@@

\item	L460: "but such information would be not be completely orthogonal" duplicate "be"

\textcolor{blue}{Reply: The duplicate word is removed. }\\

\item	
		Table 1: NEDT are constructor specifications, the real noise is lower, see
		Fig 5 Guo, Y., J. Y. He, S. Y. Gu, and N. M. Lu, 2019: Calibration and validation of
		Feng Yun-3-D microwave humidity sounder II. \\
		IEEE Geoscience and Remote Sensing
		Letters, doi:10.1109/LGRS.2019.2957403.
		Tab 5 Carminati, F., Atkinson, N., Candy, B., Lu, Q.: Insights into the Microwave Instruments Onboard the Feng-Yun 3D Satellite: Data Quality and Assimilation in the Met Office NWP System. Adv. Atmos. Sci. (2020). https://doi.org/10.1007/s00376-020-0010-1 \\

\textcolor{blue}{Reply: The reviewer rightly mentions that the real noise is lower, however we add the sensor noise according to the constructor specifications. This can be viewed as a conservative estimate of the sensor noise to include other sources of error not accounted for in NEDT. For example in study \citet{Carminati-fy3d-2020} the authors describe radiation leak affecting the higher frequency channels.}

@@

\end{itemize}

\section*{Questions}
\begin{itemize}

\item	
		Is this method applicable to IR e.g. to an ATOVS system?\\

\textcolor{blue}{Reply:  Yes, the method could potentially be applied to IR. The operation and  performance of the cloud correction approach is based on the fact that different frequencies have varying sensitivity to cloud signatures in the same field of view. For IR, infact this feature is regularly used to flag out cloud contamination. Most cloud flagging schemes for IR are based on brightness temperature thresholds.
}\\

\item 		
		The authors explain that it could benefit the all-sky assimilation systems indirectly for
		the analysis increment. Instead (or in addition) could it be used to model the variable
		observation error (when and by how much to be inflated)? This would be, in my view,
		the most valuable.	\\

\textcolor{blue}{Reply: The reviewer has a very good point. At ECMWF, the observational errors for MHS and MWHS-2 are defined as quadratic functions of symmetric cloud indicator \citep{geer2015scatteringindex}. The observational errors are higher in regions for cloud and vice-versa. Thus it could be potentially feasible to use the QRNN identified cloud impact to formulate the observational errors.  This could probably be the best use of the QRNN technique for all-sky. Of course using QRNN to develop a full observational model, would require to characterize the performance of the scheme over upper latitudes, land and ocean.}\\

\item	Could the uncertainty use for weak constraint 4dvar?\\

\textcolor{blue}{Reply: Although, the uncertainties obtained from QRNN do not have a direct application to weak constraint 4dvar, but they could still be considered as a diagnostic to help evaluate the weak constraint in the troposphere. For example, undiagnosed cirrus contamination in the upper troposphere might be associated with apparent model biases that are actually caused by systematic forward model errors. }\\

\item	
		What is the resource cost of this method (is this fast enough to be used in 1-h regional
		nwp with 30min window)?\\

\textcolor{blue}{Reply:  Yes, it would be feasible to implement the scheme into existing NWP models. In this study, QRNN was not optimized to get the maximum computational performance. For each MWHS-2 channel, it took around 30 minutes to train the net on a  x86\_64, 8 CPU machine. However, with the modern computing architectures and parallel processing, a much faster computation can be expected. }\\

### 2021-02-19 Article/Review_1/response_reviewer_2.tex

\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{xcolor}

%\usepackage{showframe} %This line can be used to clearly show the new margins

\newgeometry{vmargin={30mm}, hmargin={25mm,25mm}} 
\setlength{\topskip}{0mm}

\begin{document}
\title{\textbf{Response to Reviewer 2}}
\date{}
\maketitle

The authors would like to thank the reviewer for his/her careful review and constructive comments, which we believe will help improve the content of the manuscript.  Below, under each bullet point, we provide a point by point response to each comment/question. The author responses are given in blue, and textual changes are italicised.

\section*{General Comments}
\begin{itemize}

\item 			
			As I understand it, this study uses only simulated measurements (either with or without hydrometeors included), even for MWHS-2 for which actual measurements are available. This should be made clearer, especially given line 66, which states that no``background'' data is required for the method. I'd also like to see a bit more discussion 	about whether the results you present should be expected to hold for real data. An assumption that you are making is that your forward model can represent real clouds with enough fidelity that a model trained on simulated data will still work on real-world data. Can you point to any evidence to back up this assumption? Have you tried comparing the histograms of model-simulated Tbs with real-world MWHS-2 Tbs?\\

\textcolor{blue}{Reply: We agree with the reviewer, the line 66, can be confusing. We have re-written the sentence to:\\
Pg 3, line 68:	``\textit{This is done for each channel separately and by only using the measurements, although the scheme is demonstrated in the study by using simulated observations.}''\\\\		
Regarding the discussion about simulations holding well for the real-data, we agree with the reviewer that our assumption is a strong one and requires some evidence. For MWHS-2, we have added a new figure (Pg 6, Fig. 1, also shown below) comparing the histograms of background and bias corrected observations for one of the lower peaking channels of 183 GHz channel.  The main deviations in the distributions arise from the hydrometeor scattering. With limited scope of particle size and shape variation in current NWP microphysical schemes, the true cloud variability cannot be  described accurately, and a bias correction is necessary to be closer to the reality. Also, ECMWF has real time monitoring of many satellite sensors including FY-3D MWHS-2, thus it is possible to assess how well the system (and RTTOV-SCATT) is performing.
\newline
For ICI and SMS, though a qualitative assessment of the simulations is not possible, we expect underestimation of the cloud variability owing to only single PSD and habit assumption. However, it is important to consider that QRNN can easily adapt to changes in brightness temperatures introduced by PSD and habit variation.\\
We have added this discussion in the revised manuscript in Sect 2.2. }\\
\begin{figure}
	\centering
\includegraphics[width = 80mm]{fig00.pdf}
\caption{Probability distribution functions (PDFs) of simulated and observed brightness temperatures for MWHS-2 channel 14. The data covers latitude range $60^{\circ}$\,S to $60^{\circ}$\,N, and satellite zenith angle less than $7.5^{\circ}$.}
\end{figure}

\item  	
			What is the computational cost of the QRNN method compared to simpler cloud-
			clearing filters? Could it feasibly be implemented into existing NWP models given
			current computational constraints?\\

\textcolor{blue}{Reply: Yes, it would be feasible to implement the scheme into existing NWP models. In this study, QRNN was not optimized to get the maximum computational performance. For each MWHS-2 channel, it took around 30 minutes to train the net on a  x86\_64, 8 CPU machine. For ICI and SMS, with smaller training dataset, the time was lower. However, with the modern computing architectures and parallel processing, a much faster computation can be expected. }\\

\item  
			Lines 135-143: Why the large difference in number of cases simulated for ICI (220\,000)
			vs. SMS (143\,000), if they are both coming from the same population of CloudSat
			profiles? For the training dataset, you use about 75\% of total cases for MWHS-2,
			about 80\% of cases for ICI, and about 84\% of cases for SMS. Why this difference in
			proportions?\\

\textcolor{blue}{Reply: Yes, both ICI and SMS simulations come from same population of Cloudsat. For SMS, we had access to a smaller database, which was used for a earlier study. Due to difference in sizes of the available observations, maximum possible observations were incorporated in the training data to allow cloud variability. Even with differences in the database sizes, the results show that the predicted quantiles are well calibrated for all three sensors. With a larger database, one could expect similar or even better performance.}\\

\item  
			Line 340: ``With a test dataset of 70 000 samples, we cannot represent the far wings of the distribution accurately.'' Couldn't one apply this same reasoning to Figures 2,3, or
			8, which have density values below $10^{-4}$ included?\\

\textcolor{blue}{Reply: Yes one could apply the same reasoning to the Figures 2, 3, or 8, but we prefer to show the complete distribution to emphasize that the cases with large errors occur infrequently.}\\

\item 
			Figure 13: I wonder if there might be an easier, more concise way to evaluate whether
			the uncertainty intervals are properly calibrated. Namely, could you simply calculate
			how often the true value falls within the $\pm2\sigma$ uncertainty range, for each of the uncertainty bins ($0 - 3$K, $3 - 8$K, $8 +$ K) that you've included on the plot? If this percentage is significantly less than 95\%, it would suggests that your uncertainties are too small, while if it were closer to 100\% it would suggest your uncertainties are too large. Even if you don't get rid of Fig. 13, I think this would be useful information to include in the paper.\\

\textcolor{blue}{Reply: As per suggestion of the reviewer, we have included the information highlighting how well calibrated the uncertainties are. We provide the occurence percentage of true value for each uncertainty bin and add this information in Fig. 13 (also shown above). For each bin considered, the true value falls in the range almost 94\% of the time, indicating that the uncertainties are well calibrated. Only for channel I3V and the outermost bin, occcurence percentage is 88\%. \\	
These results are in line with Fig.7 and Fig.11, which also indicate that the uncertainty intervals are well calibrated.} \\
\begin{figure}
	\centering
	\includegraphics[width = 190mm]{fig13.pdf}
	\caption{Distribution of errors binned according to their uncertainty. The occurrence of true value in each uncertainty interval bin is given in the parentheses. Results are from QRNN-single for channels I1V, I2V and I3V.}
\end{figure}
\item  
			Lines 498-499: ``. . . other underlying uncertainties not considered here.'' Whether here or elsewhere in the paper, I think you should talk a bit more about what these other uncertainties are (radiative transfer model errors should certainly be discussed), and what effects they might have on your results.\\

\textcolor{blue}{Reply: Among the errors which affect the radiative transfer calculations are underestimation of cloud variability due to limited particle size distribution (PSD) and habit variation. Other factors include neglected antenna pattern and the limitations associated with input data, both Cloudsat and ERAInterim. For example, the simulations could have tendency to be biased towards the Cloudsat geographical sampling. All these issues can contribute to mapping errors between 183\,GHz  and higher frequency channels. However, it is possible improve the cloud representation by incorporating PSD and habit variation, and QRNN based cloud correction can easily adapt to changes in brightness temperatures introduced by the local variability.  This is not the case with all-sky data assimilation systems, which assume only single PSD and habit combination, and shall continue to do so in coming years.\\
We have edited Sect 2.2 and Conclusions to describe these different errors and their implications.  }

### 2021-02-19 Article/ici_submm_cloudcorr_v1.1.tex
response to reviewer v1

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder-2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1.0      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3.0      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7.0      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D. MWHS-2 is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}. The channels relevant to this study are described in Table~\ref{tab:specifications_MWHS2}.

For this study, MWHS-2 simulations were sourced from the operational ECMWF assimilation system.

@@

\subsection{Simulations}
%
MWHS-2 simulated radiances during the period June--July 2020 are sourced from ECMWF. In the current version of the ECMWF Integrated Forecasting System (IFS), cycle 47R1 \citep{IFS47R1chap1}, clear-sky and all-sky radiative transfer are performed simultaneously for monitoring purposes, despite all humidity sounders being assimilated via all-sky exclusively. These side by side radiative transfer calculations on a large variety of model scenes provides an ideal dataset for comparing radiances with and without cloud effects. Out of all the available observations during the period, we use data for the latitudinal range: $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle, less than $7.5^{\degree}$. With this filter, we have approximately 290\,000 cases.

@@

@@

To conclude the results, we analyse if the uncertainty estimates given by QRNN are representative of prediction accuracy. Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed ICI errors binned by their corresponding uncertainty in $\pm\,2\sigma$  confidence interval. For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the prediction increases. The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm\,$2.5\,K. With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors. Poor predictions occur more frequently when uncertainty is high. Cases with accurate predictions yet high uncertainty are also present. In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties follow the same relationship. Similar results are also obtained with SMS (not shown).

@@

The cloud corrected radiances have great potential in both retrieval schemes and numerical weather prediction (NWP) systems. Even with availability of new sensors and better observations, the problems posed by undetected cloud impact limit the complete usage of humidity observations. However, with the cloud correction methodology presented here, we can aim at resolving these limitations. This is especially true for clear-sky assimilation systems, which reject up to 80\,\% of the available observations due to cloud contamination. In fact, one of reasons for the positive performance of all-sky assimilation systems is attributed to the larger number of assimilated observations in comparison to clear-sky observations. If QRNN can provide the clear-sky NWP systems with cloud cleared microwave radiances with minimal rejection of data, it may be possible to reap forecast benefits without additional complexities and computational cost of scattering calculations. The all-sky assimilation systems could also benefit indirectly from cloud corrected radiances, to provide a measure of cloud impact as a diagnostic field for analysing increments. Another advantage of combining 183\,GHz and sub-mm for cloud correction is that NWP systems, which are not yet prepared for higher frequency channels, could still benefit from the data early on.

In this study, we demonstrate the correction scheme with data from a limited period. The seasonal and latitudinal distributions are not taken into account, and more complex surfaces such as sea ice, snow, and high orography have not been considered. It remains to be seen whether QRNN shows any seasonal sensitivity or dependency on cloud types. Such analysis could also be important at improving the a priori distribution of rare cases.

@@

\appendix
\section{ARTS setup}    %% Appendix A
\label{appendix:ARTS_setup}
%
All radiative transfer forward simulations are made by the Atmospheric Radiative
Transfer System \citep[ARTS,][]{eriksson:arts2:11,buehler:artst:18}), version
arts-2.3.1. All simulations are based on dBZ-based model system presented by \citet{ekelund2020using}, i.e.\ CloudSat reflectivities are used as input and are converted to ice water content (IWC) and rain water content (RWC) using microphysical assumptions. For each atmospheric case, both all-sky and clear-sky calculations are performed. In the former, all hydrometeors contents are set to zero, while in the latter, IWC and RWC derived from CloudSat reflectivities, and liquid water content (LWC) from ERA-Interim \citep{dee2011erainterim} are included. In order to avoid a possible bias between clear-sky and all-sky calculations for insignificant hydrometeor contents, both calculations are made by the RT4 solver \citep{evans1995microwavec}. The absorption model takes into account the effect from nitrogen
\citep{pwr:93}, oxygen \citep{pwr:93}, liquid water content \citep[LWC,][]{ellison2007permittivity}, and water vapour. For water vapour, absorption model as  in RTTOV \citep[Radiative transfer for TOVS,][]{saunders2018update} is followed, but with few modifications \citep{turner2019amsutran}. LWC is assumed to be totally absorbing. In the mapping of CloudSat reflectivities to RWC and IWC, a total separation between liquid and ice phase is assumed. All scattering hydrometeors at temperatures above 0$^{\degree}$C  and below 0$^{\degree}$\,C are assumed to be rain and ice hydrometeors respectively. For RWC, the particle size distribution (PSD) of \citet{abel2012improved} is applied. The PSD of IWC follows the basic formulation applied in DARDAR \citep[\url{
	http://www.icare.univ-lille1.fr/projects/dardar}][]{delanoe2008variational}, using latest parameter values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
This PSD can be considered as a ``two moment'' scheme, but is here applied in a one moment manner by setting $N_0^*$ (as a function of temperature)
following Table~5 of \citet{delanoe2014normalized}, and letting the radar reflectivity set the remaining moment. Single scattering data are taken from
\citet{eriksson:agene:18}. For ice hydrometeors, three habits are applied:
perpendicular 3-bullet rosette, large plate aggregate and large column
aggregate. In the last two cases, the aggregates are complemented with single crystal data to also cover smaller sizes. The particles are assumed to have a totally random orientation. 
To apply oriented particles is much more computationally costly and could not be accommodated inside the study. The land emissivity was taken from Tool to Estimate Land‐Surface Emissivities at Microwave frequencies \citep[TELSEM,][]{aires2011tool} and the
Ocean/water from Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves \citep[TESSEM,][]{prigent2017sea}.

>>>>

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder-2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1.0      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3.0      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7.0      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D. MWHS-2 is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}.

For the demonstration of the study, MWHS-2 background observations or simulations are used. Actual measurements are not taken into account. The requisite data was obtained from ECMWF. More details are described in Sect.~\ref{simulations}.

@@

\subsection{Simulations}
%
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig00.pdf} 
	\caption{Probability distribution functions (PDFs) of simulated and observed brightness temperatures for MWHS-2 channel 14. The data covers latitude range $60^{\degree}$\,S to $60^{\degree}$\,N, and satellite zenith angle less than $7.5^{\degree}$.}
	\label{fig:distribution_OB_mwhs14}	
\end{figure}
\label{simulations}
MWHS-2 simulated radiances during the period June--July 2020 are sourced from ECMWF. In the current version of the ECMWF Integrated Forecasting System (IFS), cycle 47R1 \citep{IFS47R1chap1}, clear-sky and all-sky radiative transfer are performed simultaneously for monitoring purposes, despite all humidity sounders being assimilated via all-sky exclusively. These side by side radiative transfer calculations on a large variety of model scenes provides an ideal dataset for comparing radiances with and without cloud effects. Out of all the available observations during the period, we use data for the latitudinal range: $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle, less than $7.5^{\degree}$. With this filter, we have approximately 290\,000 cases. Figure~\ref{fig:distribution_OB_mwhs14} shows the histogram of background and bias corrected observations for MWHS-2 channel 14. The part of the distribution matching clear-sky conditions shows a good agreement between the background and the observations. The main deviations in the distributions arise from the hydrometeor scattering. With limited scope of particle size and shape variation in current NWP microphysical schemes, the true cloud variability cannot be  described accurately, and a bias correction is necessary to be closer to reality.

@@

For ICI and SMS, the cloud variability  is incorporated by randomly selecting between three habits and one particle size distribution (PSD) (see Appendix~\ref{appendix:ARTS_setup}). But with only one PSD, the true hydrometeor variability will be underestimated. Underestimation of scattering at higher frequencies can lead to some imperfections in mapping the cloud information from sub-mm and 183\,GHz. Other factors affecting the accuracy of simulations, but not considered due to brevity, include neglected antenna pattern and limitations associated with input data, both Cloudsat and ERAInterim. For example, the simulations could have tendency to be biased towards the Cloudsat geographical sampling. The actual background departures and the corresponding bias correction shall only be revealed when data from ICI is available in future.

@@

To conclude the results, we analyse if the uncertainty estimates given by QRNN are representative of prediction accuracy. Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed ICI errors binned by their corresponding uncertainty in $\pm\,2\sigma$  confidence interval. For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the prediction increases. The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm\,$2.5\,K. With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors. Poor predictions occur more frequently when uncertainty is high. Cases with accurate predictions yet high uncertainty are also present. For each channel and bin, but last bin for I3V,  the occurrence of true value inside all three uncertainty bins is almost 94\%, indicating that uncertainties are well calibrated and are not concentrated in a narrow interval. Only for I3V, the uncertainties are slightly smaller in the last bin. In spite of individual variations in the error distributions for each channel, the predictions and their corresponding uncertainties follow the same relationship. Similar results are also obtained with SMS (not shown).

@@

The cloud corrected radiances have great potential in both retrieval schemes and numerical weather prediction (NWP) systems. Even with availability of new sensors and better observations, the problems posed by undetected cloud impact limit the complete usage of humidity observations. However, with the cloud correction methodology presented here, we can aim at resolving these limitations. This is especially true for clear-sky assimilation systems, which reject up to 80\,\% of the available observations due to cloud contamination. In fact, one of reasons for the positive performance of all-sky assimilation systems is attributed to the larger number of assimilated observations in comparison to clear-sky observations. If QRNN can provide the clear-sky NWP systems with cloud cleared microwave radiances with minimal rejection of data, it may be possible to reap forecast benefits without additional complexities and computational cost of scattering calculations. The all-sky assimilation systems could also benefit indirectly from cloud corrected radiances, to provide a measure of cloud impact as a diagnostic field for analysing increments. Also, it could be potentially feasible to use the QRNN identified cloud impact to formulate the observational errors. This could probably be the best use of the QRNN technique for all-sky. Another advantage of combining 183\,GHz and sub-mm for cloud correction is that NWP systems, which are not yet prepared for higher frequency channels, could still benefit from the data early on.

In this study, we demonstrate the correction scheme with data with limited cloud variability and also neglect the antenna pattern. With only one habit and PSD, the true variability of the hydrometeors could be underestimated and can introduce mapping errors between 183\,GHz and sub-mm channels. However, it is possible improve the cloud representation by incorporating PSD and habit variation, and QRNN based cloud correction can easily adapt to changes in TB introduced by the local variability.  This is not the case with all-sky DA systems, which assume only single PSD and habit combination, and shall continue to do so in coming years. Additionally, in the limited period study, the seasonal and latitudinal distributions are also not taken into account, and more complex surfaces such as sea ice, snow, and high orography have not been considered. It remains to be seen whether QRNN shows any seasonal sensitivity or dependency on cloud types. Such analysis could also be important at improving the a priori distribution of rare cases.

@@

\appendix
\section{ARTS setup}    %% Appendix A
\label{appendix:ARTS_setup}
%
All radiative transfer forward simulations are made by the Atmospheric Radiative
Transfer System \citep[ARTS,][]{eriksson:arts2:11,buehler:artst:18}), version
arts-2.3.1. All simulations are based on dBZ-based model system presented by \citet{ekelund2020using}, i.e.\ CloudSat reflectivities are used as input and are converted to ice water content (IWC) and rain water content (RWC) using microphysical assumptions. For each atmospheric case, both all-sky and clear-sky calculations are performed. In the former, all hydrometeors contents are set to zero, while in the latter, IWC and RWC derived from CloudSat reflectivities, and liquid water content (LWC) from ERA-Interim \citep{dee2011erainterim} are included. In order to avoid a possible bias between clear-sky and all-sky calculations for insignificant hydrometeor contents, both calculations are made by the RT4 solver \citep{evans1995microwavec}. The absorption model takes into account the effect from nitrogen
\citep{pwr:93}, oxygen \citep{pwr:93}, liquid water content \citep[LWC,][]{ellison2007permittivity}, and water vapour. For water vapour, absorption model as  in RTTOV \citep[Radiative transfer for TOVS,][]{saunders2018update} is followed, but with few modifications \citep{turner2019amsutran}. For 22 and 183\,GHz transitions, some parameters are replaced. A small comparison with RTTOV shows an agreement of the order of 0.1\,K. LWC is assumed to be totally absorbing.  While mapping the CloudSat reflectivities to RWC and IWC, the liquid and ice phase are assumed to be totally separated. All scattering hydrometeors at temperatures above 0$^{\degree}$C are assumed to be rain and below 0$^{\degree}$\,C as ice hydrometeors. For RWC, the particle size distribution (PSD) of \citet{abel2012improved} is applied. The PSD of IWC follows the basic formulation applied in DARDAR \citep[\url{
	http://www.icare.univ-lille1.fr/projects/dardar}][]{delanoe2008variational}, using latest parameter values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
This PSD can be considered as a ``two moment'' scheme, but is here applied in a one moment manner by setting $N_0^*$ (as a function of temperature)
following Table~5 of \citet{delanoe2014normalized}. The remaining moment is set by the radar reflectivity. Single scattering data are taken from
\citet{eriksson:agene:18}. For ice hydrometeors, three habits are applied:
perpendicular 3-bullet rosette, large plate aggregate and large column
aggregate. In the last two cases, the aggregates are complemented with single crystal data to also cover smaller sizes. The particles are assumed to have a totally random orientation. 
It is computationally much expensive to apply oriented particles and are not accommodated inside the study. The land emissivity was taken from Tool to Estimate Land‐Surface Emissivities at Microwave frequencies \citep[TELSEM,][]{aires2011tool} and the
Ocean/water from Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves \citep[TESSEM,][]{prigent2017sea}.
